---
title: "Apathy and Physical Activity: Meta-Analysis"
author: "Lahart IM, Boisgontier MP"
date: "`r format(Sys.Date(),'%e de %B, %Y')`"
output:
  pdf_document:
    latex_engine: xelatex
    toc: yes
    toc_depth: 3
---
<style>
body{
  font-size: 8pt;
}
</style>
---

# R Markdown file set-up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r import data file, include=FALSE}
apathy_r <- read.csv("PA_Apathy_r.csv", 
                      header = TRUE, sep = ",")
apathy_rho <- read.csv("PA_Apathy_rho.csv", 
                      header = TRUE, sep = ",")
```

Packages required:
1) dmetar
2) tidyverse
3) meta
4) metafor
5) metasens
6) esc

```{r install and load dmetar, include=FALSE}
if (!require("devtools")) {
  install.packages("devtools")
}
devtools::install_github("MathiasHarrer/dmetar")
library(dmetar)
```

```{r packages, include=FALSE}
#Install tidyverse package if needed for 'glimpse'
if(!require(tidyverse)){install.packages('tidyverse')}
#Load tidyverse package
library(tidyverse)

#Install meta package if needed for meta-analysis
if(!require(meta)){install.packages('meta')}
#Load meta package
library(meta)

#Install metafor package if needed for meta-analysis
if(!require(metafor)){install.packages('metafor')}
#Load metfor package
library(metafor)

#Install dmetar package if needed for meta-analysis
if(!require(dmetar)){install.packages('dmetar')}
#Load metfor package
library(dmetar)

#Install metasens package if needed for meta-analysis
if(!require(metasens)){install.packages('metasens')}
#Load metfor package
library(metasens)

#Install esc package if needed for Fisher z conversion to r
if(!require(esc)){install.packages('esc')}
#Load esc package
library(esc)
```

# Data file glimpse (not included in PDF)

```{r glimpse, include=FALSE}
glimpse(apathy_r)
glimpse(apathy_rho)
```

# Meta-analysis method

In a meta-analysis, we pooled Pearson product-moment correlations from eligible studies to examine the relationship between apathy and physical activity. Correlations were pooled using the generic inverse pooling method via the ‘metacor’ function in the R ‘meta’ package (Schwarzer et al., 2023a). This function automatically performs a necessary Fisher’s z-transformation on the original, untransformed correlations prior to pooling. The ‘metacor’ function also reconverts the pooled association back to its original form for ease of interpretation. We used the ‘metafor’ package (Vietchbauer, 2010, 2023) to compare our three-level model to one in which a level was removed to investigate if our three-level model represented the variability in our data better than a two-level model. We anticipated considerable between-study heterogeneity, and therefore used a random-effects model to pool correlations. The restricted maximum likelihood (RML) estimator (Viechtbauer et al., 2005) was used to calculate the heterogeneity variance Tau2. In addition to Tau2, to quantify between study heterogeneity, we report the I2 statistic, which provides the percentage of variability in the correlations that is not caused by sampling error (Higgins et al., 2002). The I2 statistic was interpreted as follows: 0-40%, may not be important; 30-60%, may represent moderate heterogeneity; 50-90%, may represent substantial heterogeneity; and 75-100%, may represent considerable heterogeneity. To reduce the risk of false positives, we used a Knapp-Hartung adjustment (Knapp et al.,2003) to calculate the confidence interval around the pooled association. We also report the prediction interval, which provides a range within which we can expect the associations of future studies to fall based on the current evidence. The pooled correlation was interpreted using Cohen’s conventions (Cohen et al., 1998): r ≈ -0.10, small negative correlation; r ≈ -0.30, moderate negative correlation; r ≈ -0.50, large negative correlation. Egger’s regression test of funnel plot asymmetry (Egger et al., 1997) and a p-curve analysis (Simonsohn et al., 2014) were conducted to assess potential publication bias in our meta-analysis.

A secondary meta-analysis was conducted using the same approach, but based on Spearman’s rho values, to further test the relationship between apathy and physical activity.

Subgroup analyses were conducted to examine the differences in correlations between studies including participants with different health conditions and using different types of physical activity outcomes, and apathy measures.

Meta-regressions were conducted to examine if the average age of participants or the proportion of women in a study predicted the reported correlation between apathy and physical activity. Another meta-regression was used as a sensitivity analysis to examine whether the quality of the studies affected the correlation.

All analyses were performed in RStudio integrated development environment (IDE) (2023.06.1+524, “Mountain Hydrangea” release) for R software environment (R Core Team, 2023) using the ‘meta’ (Schwarzer, 2023a), ‘metasens’ (Schwarzer et al., 2023b), and ‘metafor’ (Vietchbauer, 2010, 2023) R packages.


# Meta-analysis: primary analysis

```{r meta-analysis RE REML and Knapp-Hartung adjustment}
m.cor <- metacor(cor = cor, 
                 n = n,
                 studlab = author,
                 data = apathy_r,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE,
                 title = "Apathy and physical activity behaviour")
summary(m.cor)
```

Our meta-analysis of 14 studies (n = 1220) based on Pearson’s r revealed a statistically significant small to moderate negative correlation between apathy and physical activity (r = -0.17; 95% confidence interval [95% CI]: -0.24 to -0.10; p = 0.0002). Further supporting this result, between-study statistical heterogeneity could be considered as not important (Tau2 = 0.004, 95% CI: 0.000 to 0.032; I2 = 18.1%, 95% CI: 0.0 to 55.8%), and the prediction interval ranged from r = -0.32 to -0.02, suggesting that the true effect size is at least small, and that the correlation is expected to be negative for a future study.


```{r Forest plot apathy and PA, fig.height=5, fig.width=10}
forest(m.cor, 
            layout = "Revman5",
            sortvar = -TE,
            prediction = TRUE, 
            print.tau2 = FALSE,
            leftlabs = c("Author", "n"),
            xlim=c(-1.0,1.0),
            fs.hetstat = 10,
            addrows.below.overall = 2)
```

```{r Save Forest plot main analysis}
png(file = "Main analysis forestplot.png", 
    width = 2800, height = 3800, res = 300)

forest(m.cor, 
            layout = "Revman5",
            sortvar = -TE,
            prediction = TRUE, 
            print.tau2 = FALSE,
            leftlabs = c("Author", "n"),
            xlim=c(-1.0,1.0),
            fs.hetstat = 10,
            addrows.below.overall = 2)

dev.off()
```


# Secondary analysis based on Spearman's rho values

## Analysis with metafor with model comparisons

```{r secondary meta-analysis RE REML using metafor}
mv.cor.rho <- rma.mv(yi = z, 
                V = var.z, 
                slab = author,
                data = apathy_rho,
                random = ~ 1 | author/cor_id,
                test = "t", 
                method = "REML")
summary(mv.cor.rho)
```

```{r Convert Fisher z back to Pearsons r}
round(convert_z2r(-0.4275), 3) # point estimate
round(convert_z2r(-0.8381), 3) # lower CI
round(convert_z2r(-0.0169), 3) # Upper CI
```

### Explore heterogeneity

```{r Heterogeneity}
i2 <- var.comp(mv.cor.rho)
summary(i2)
plot(i2)
```

### Comparing models

Reduced model in which the level 3 variance (between study heterogeneity) is set to 0, which assumes all effect sizes are independent.

```{r level 3 variance set to zero}
l3.removed <- rma.mv(yi = z, 
                     V = var.z, 
                     slab = author,
                     data = apathy_rho,
                     random = ~ 1 | author/cor_id,
                     test = "t", 
                     method = "REML",
                     sigma2 =  c(0, NA))

summary(l3.removed)
```

Comparing full and reduced models.

```{r Comparison of models}
anova(mv.cor.rho, l3.removed)
```

## Secondary analysis of rho values with meta

```{r Secondary meta-analysis based on rho values}
m.cor.rho <- metacor(cor = cor, 
                 n = n,
                 data = apathy_rho,
                 cluster = cluster,
                 studlab = author,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE)
summary(m.cor.rho)
```


Results of the secondary meta-analysis based on seven Spearman rho values (k = 4, n = 543) were consistent with those based on Pearson’s r as they showed a statistically significant moderate negative correlation between apathy and physical activity (r = -0.40; 95% CI: -0.68 to -0.02; p = 0.043). However, we observed substantial to considerable between-study statistical heterogeneity (between-cluster Tau2 = 0.09, 95% CI: 0.01 to 0.97; I2 = 82.0%, 95% CI: 64.1 to 91.0%), and the prediction interval ranged from r = -0.87 to 0.45, indicating that a moderate positive correlation cannot be ruled out for future studies.


```{r Secondary analysis forest plot based, fig.height=4, fig.width=10, warning=FALSE}
forest(m.cor.rho, 
            layout = "Revman5",
            sortvar = -TE,
            prediction = TRUE, 
            print.tau2 = FALSE,
            fontsize = 11,
            xlim=c(-1.0,1.0),
            fs.hetstat = 10,
            addrows.below.overall = 2)
```


```{r Save Forest plot rho analysis, warning=FALSE}
png(file = "Rho analysis forestplot.png", 
    width = 2500, height = 2000, res = 300)

forest(m.cor.rho, 
            layout = "Revman5",
            sortvar = -TE,
            prediction = TRUE, 
            print.tau2 = FALSE,
            fontsize = 11,
            xlim=c(-1.0,1.0),
            fs.hetstat = 10,
            addrows.below.overall = 2)

dev.off()
```


# Meta-analysis: subgroup analyses

## Subgroup analysis by health status

```{r Subgroup analysis by health status}
apathy_r$Health_status <- as.factor(apathy_r$Health_status)

Health_subg <- update(m.cor, 
            subgroup = Health_status,
            tau.common = FALSE)
Health_subg
```

The test of subgroup differences between health status measures was possible between studies comprising people with Parkinson (k = 4), stroke (k = 2), and older adults with cognitive impairment (k = 2). We found statistical differences between these studies (p = 0.0002). The relationship between apathy and physical activity was statistically significant only in studies that included participants with Parkinson's disease (r = -0.22; 95% CI: -0.29 to -0.12). 

```{r Forest plot for subgroup by Health condition, fig.height=10, fig.width=8}
forest(Health_subg,
            layout = "Revman",
            sortvar = -TE, 
            common = FALSE, 
            xlim = c(-1, 1), 
            prediction = TRUE, 
            fontsize = 11,
            fs.hetstat = 10, 
            col.subgroup = 'black',
            addrows.below.overall = 2)
```

```{r Save Health condition forestplot}
png(file = "Health condition forestplot.png", 
    width = 2800, height = 3000, res = 300)

forest(Health_subg, 
            layout = "Revman",
            sortvar = -TE, 
            common = FALSE, 
            xlim = c(-1, 1), 
            prediction = TRUE, 
            fontsize = 11,
            fs.hetstat = 10, 
            col.subgroup = 'black',
            addrows.below.overall = 2)

dev.off()
```


## Subgroup analysis by physical activity outcome

```{r Subgroup analysis by PA outcome}
apathy_r$PA_outcome <- as.factor(apathy_r$PA_outcome)

PAout_subg <- update(m.cor, 
            subgroup = PA_outcome, 
            tau.common = FALSE)
PAout_subg
```

The test of subgroup differences between physical activity outcomes was possible between studies using active time per day or week (k = 5), MET-min/week (k = 4), or a score from a questionnaire (k = 3). We found statistical difference between these studies (p = 0.006), with only the studies using active time per day or week (r = -0.22; 95% CI: -0.30 to -0.14) and a score from a questionnaire (r = -0.27; 95% CI: -0.39 to -0.14) showing a statistically significant correlation.


```{r PA outcome subgroup forest plot, fig.height=8, fig.width=8}
forest(PAout_subg, 
            layout = "RevMan5", 
            sortvar = -TE, 
            common = FALSE, 
            xlim = c(-1.0, 1.0), 
            prediction = TRUE, 
            fontsize = 11,
            fs.hetstat = 10,  
            col.subgroup = 'black',
            addrows.below.overall = 2)
```

```{r Save PA outcome forestplot}
png(file = "PA outcome forestplot.png", 
    width = 2800, height = 3200, res = 300)

forest(PAout_subg, 
             layout = "RevMan5", 
            sortvar = -TE, 
            common = FALSE, 
            xlim = c(-1.0, 1.0), 
            prediction = TRUE, 
            fontsize = 11,
            fs.hetstat = 10,  
            col.subgroup = 'black',
            addrows.below.overall = 2)

dev.off()
```


## Subgroup analysis by apathy measure

```{r Subgroup analysis by apathy measure}
apathy_r$Apathy <- as.factor(apathy_r$Apathy)

apathy_subg <- update(m.cor, 
            subgroup = Apathy, 
            tau.common = FALSE)
apathy_subg
```

The test of subgroup differences between apathy measures was possible between studies using the Apathy Scale (k = 7) and the Apathy Evaluation Scale (k = 5). We observed no evidence of a statistical difference between these measures (p = 0.09), with only both studies using the Apathy Scale (r = -0.12; 95% CI: -0.24 to -0.10) and the Apathy Evaluation Scale (r = -0.23; 95% CI: -0.35 to -0.11) showing a statistically significant correlation.

```{r Forest plot for subgroup by apathy measure, fig.height=8, fig.width=8}
forest(apathy_subg, 
            layout = "Revman5", 
            sortvar = -TE, 
            common = FALSE, 
            xlim = c(-1, 1), 
            prediction = TRUE, 
            fontsize = 11,
            fs.hetstat = 10, 
            col.subgroup = 'black',
            addrows.below.overall = 2)
```

```{r Save Apathy measure forestplot}
png(file = "Apathy measure forestplot.png", 
    width = 2800, height = 3200, res = 300)

forest(apathy_subg, 
            layout = "Revman5", 
            sortvar = -TE, 
            common = FALSE, 
            xlim = c(-1, 1), 
            prediction = TRUE, 
            fontsize = 11,
            fs.hetstat = 10, 
            col.subgroup = 'black',
            addrows.below.overall = 2)

dev.off()
```


# Meta-analysis: meta-regression

## Meta-regression by age

```{r Meta-regression by age}
m.cor.reg.age <- metareg(m.cor, ~Age)
m.cor.reg.age
```

Age statistically influenced the correlation values of the meta-analysis studies (k = 9; p = 0.0009). 

```{r Bubble plot for meta-regression by age, fig.height=6, fig.width=6}
Age.bubble <- bubble(m.cor.reg.age, 
                     xlim = c(35, 85), 
                     ylim = c(-1.0, 0.5),
                     xlab = 'Age (years)',
                     font.lab = 2,
                     studlab = TRUE, 
                     cex = 2, 
                     cex.studlab = 0.5, 
                     pos.studlab = 4, 
                     offset = 0.5, 
                     col.line = 'red')

Age.bubble
```


```{r Save age bubble plot}
png(file = "Bubble plot for meta-regression by age.png", 
    width = 2500, height = 2500, res = 300)

Age.bubble

dev.off()
```


## Meta-regression by proportion of women

```{r Meta-regression by proportion of women}
m.cor.reg.women <- metareg(m.cor, ~Prop_women)
m.cor.reg.women
```

Conversely, the proportion of women (k = 9) did not statistically influence the meta-analysis studies' correlation values.

```{r Bubble plot for meta-regression by proportion of women, fig.height=6, fig.width=6}
Propwomen.bubble <- bubble(m.cor.reg.women, 
       xlim = c(0.1, 0.9), 
       ylim = c(-1, 0.5), 
       xlab = 'Proportion of women',
       font.lab = 2,
       studlab = TRUE, 
       cex = 2, 
       cex.studlab = 0.5, 
       pos.studlab = 4, 
       offset = 0.5, 
       col.line = 'red')

Propwomen.bubble
```

```{r Save prop women bubble plot}
png(file = "Bubble plot for meta-regression by proportion of women.png", 
    width = 2500, height = 2500, res = 300)

Propwomen.bubble

dev.off()
```

# Sensitivity analysis: meta-regression by axis score

```{r Meta-regression by axis score}
m.cor.reg.axis <- metareg(m.cor, ~ Q_score)
m.cor.reg.axis
```

The meta-regression by quality score based on the Quality Assessment Tool for Observational Cohort and Cross-Sectional Studies (k = 9) showed that a study’s quality did not influence correlation values (p = 0.813).

```{r Bubble plot for meta-regression by axis score, fig.height=6, fig.width=6}
Axis.bubble <- bubble(m.cor.reg.axis, 
                xlim = c(5, 15), 
                ylim = c(-1.0, 0.5), 
                xlab = 'axis score',
                studlab = TRUE, 
                font.lab = 2,
                cex = 1.5, 
                cex.studlab = 0.5, 
                pos.studlab = 4, 
                offset = 0.5, 
                col.line = 'red')
Axis.bubble
```

```{r Grid of bubbleplots, fig.width=12, fig.height=6}
parameter <- par(mfrow=c(1,3))

parameter <- bubble(m.cor.reg.age, 
                   xlim = c(35, 85), 
                   ylim = c(-1, 0.5),
                   xlab = 'Age (years)',
                   font.lab = 2,
                   studlab = TRUE, 
                   cex = 2, 
                   cex.studlab = 0.5, 
                   pos.studlab = 4, 
                   offset = 0.5, 
                   col.line = 'red')              

parameter <- bubble(m.cor.reg.women, 
                   xlim = c(0.1, 0.9), 
                   ylim = c(-1.0, 0.5), 
                   xlab = 'Proportion of women',
                   font.lab = 2,
                   studlab = TRUE, 
                   cex = 2, 
                   cex.studlab = 0.5, 
                   pos.studlab = 4, 
                   offset = 0.5, 
                   col.line = 'red')

parameter <- bubble(m.cor.reg.axis, 
                  xlim = c(5, 15), 
                  ylim = c(-1.0, 0.5), 
                  xlab = 'Quality score',
                  studlab = TRUE, 
                  font.lab = 2,
                  cex = 1.5, 
                  cex.studlab = 0.5, 
                  pos.studlab = 4, 
                  offset = 0.5, 
                  col.line = 'red')
```


# Publication bias analysis

## Small-study effects

### Funnel plot 

```{r Contour-enhanced funnel plot for main analysis with labels, fig.height=6, fig.width=8}
# Define fill colors for contour
col.contour = c("gray75", "gray85", "gray95")

# Funnel plot
funnel(m.cor, 
       xlim = c(-1.5, 1),
       contour = c(0.9, 0.95, 0.99),
       col.contour = col.contour,
       studlab = TRUE,
       cex = 1,
       cex.studlab = 0.5, 
       pos.studlab = 4, 
       offset = 0.5)

# legend
legend(x =0.5, y = 0.01, 
       legend = c("p < 0.1", "p < 0.05", "p < 0.01"),
       fill = col.contour)

# title
title("Contour-Enhanced Funnel Plot (Apathy and Physical Activity)")
```

```{r Contour-enhanced funnel plot for main analysis no labels, fig.height=6, fig.width=8}
# Define fill colors for contour
col.contour = c("gray75", "gray85", "gray95")

# Funnel plot
funnel(m.cor, 
       xlim = c(-1.5, 1),
       contour = c(0.9, 0.95, 0.99),        
       studlab = FALSE,
       cex = 1,
       cex.studlab = 0.5, 
       pos.studlab = 4, 
       offset = 0.5,
       col.contour = col.contour)

# legend
legend(x =0.5, y = 0.01, 
       legend = c("p < 0.1", "p < 0.05", "p < 0.01"),
       fill = col.contour)

# title
title("Contour-Enhanced Funnel Plot (Apathy and Physical Activity)")
```


```{r funnel plot for main analysis, fig.height=6, fig.width=8}
# Produce funnel plot
funnel(m.cor,
            xlim = c(-1, 0.5),
            ylim = c(0.3, 0.0),
            studlab = TRUE,
            cex = 1.5,
            cex.studlab = 0.5, 
            pos.studlab = 4, 
            offset = 0.5)
```

```{r Save funnel plot}
png(file = "Funnel Plot.png", width = 2100, height = 1500, res = 300)

# Define fill colors for contour
col.contour = c("gray75", "gray85", "gray95")

# Funnel plot
funnel(m.cor, 
       xlim = c(-1.5, 1),
       contour = c(0.9, 0.95, 0.99),
       col.contour = col.contour,
       studlab = TRUE,
       cex = 1,
       cex.studlab = 0.5, 
       pos.studlab = 4, 
       offset = 0.5)

# legend
legend(x =0.5, y = 0.01, 
       legend = c("p < 0.1", "p < 0.05", "p < 0.01"),
       fill = col.contour)

# title
title("Contour-Enhanced Funnel Plot (Apathy and Physical Activity)")

dev.off()
```

### Egger's test

```{r Eggers test for main analysis}
metabias(m.cor, method.bias = "linreg", k.min = 9)
eggers.test(m.cor)
```

Egger’s regression test does not indicate the presence of funnel plot asymmetry (b = -1.39, 95% CI: -2.69 to -0.09, p = 0.058), which suggests that publication bias is unlikely to influence the effect sizes observed in the main meta-analysis.


## Pcurve analysis
Standard errors of the correlation values were calculated using the formula: sqrt((1 - correlation_coefficient^2) / (sample_size - 2))
```{r pcurve for main analysis}
p_curve_data = data.frame("studlab" = c(paste("Study_", 1:21, sep = "")),
                 "TE" = c(-0.27, -0.057, -0.37, -0.23, -0.25, -0.18, -0.03, -0.25, 
                          -0.048, -0.12, -0.32, 0.05, -0.17, -0.08, -0.49, -0.39, 
                          -0.15, 0.01, -0.11, -0.71, -0.31),
                      
                 "seTE" = c(0.150373518685809, 0.257779104402717, 0.103225750448013, 
                            0.089212238675037,0.147656105804655, 0.176671738616584, 
                            0.162148405058939, 0.155043418, 0.217966358,      
                            0.0611010092660779, 0.095219046, 0.100378073, 0.122229293, 
                            0.064748784, 0.085479417225615, 0.090293325, 0.108522387, 
                            0.109758772, 0.109098165, 0.109977825, 0.170757326))
                  
pcurve(p_curve_data)
```
The 21 studies reporting a correlation value (Pearson’s r or Spearman’s rho) were provided to the p-curve analysis. The observed p-curve includes seven (33.3%) statistically significant results (p < 0.05), with the six of them being p < 0.025 (Figure 4). The other results were excluded because they had a p > 0.05. The p-value of the right-skewness test was < 0.001 for both the half curve and the full curve, suggesting that evidential value was present, i.e., that the effect we estimated is not spurious; an artifact caused by selective reporting (e.g., p-hacking) in the literature.



# References

- Cohen J. Statistical power analysis for the behavioral sciences. 2nd ed.; 1988.  
- Egger M, Davey Smith G, Schneider M, Minder C. Bias in meta-analysis detected by a simple, graphical test. BMJ. 1997;315(7109):629-634. https://doi.org/10.1136/bmj.315.7109.62  
- Higgins JPT, Thompson SG. Quantifying heterogeneity in a meta-analysis. Stat Med. 2002;21(11):1539-1558. https://doi.org/10.1002/sim.1186  
- Knapp G, Hartung J. Improved tests for a random effects meta-regression with a single covariate. Stat Med. 2003;22(17):2693-2710. https://doi.org/10.1002/sim.1482  
- R Core Team. R: A language and environment for statistical computing [Computer software]. Version 4.3.1. Vienna, Austria: Foundation for Statistical Computing; 2023. https://www.r-project.org 
- Schwarzer G. Meta: General package for meta-analysis [R package]. Version 6.5-0; 2023a. https://cran.r-project.org/web/packages/meta/meta.pdf 
- Schwarzer G, Carpenter RJ, Rücker G. Metasens: Advanced statistical methods to model and adjust for bias in meta-analysis [R package]. Version 1.5-2; 2023b. https://cran.r-pro-ject.org/web/packages/metasens/metasens.pdf  
- Simonsohn U, Nelson LD, Simmons JP. P-curve: A key to the file-drawer. J Exp Psychol Gen. 2014;143(2):534-547. http://doi.org/10.1037/a0033242  
- Viechtbauer W. Bias and efficiency of meta-analytic variance estimators in the random-effects model. J Educ Behav Stat. 2005;30(3):261-293. https://doi.org/10.3102/10769986030003261  
- Viechtbauer W. Conducting meta-analyses in R with the metafor package. J Stat Softw. 2010;36(3):1-48. https://doi.org/10.18637/jss.v036.i03  
- Viechtbauer W. Metafor: Meta-analysis package for R [R package]. Version 4.2-0; 2023. https://cran.r-pro-ject.org/web/packages/metafor/metafor.pdf  
- Viechtbauer, "W. (2023). Metafor: Meta-Analysis Package for R (Version 4.2-0) [R pakage]. https://cran.r-project.org/web/packages/metafor/metafor.pdf  
